\sysfull

### 2018-08-04 paper/asplos19/hwswsetup.tex

We used two platforms to evaluate \sys: (i) an \emph{intermittently-powered}
energy-harvesting device, and (i) a \emph{continuously-powered} evaluation
board.
%
Every benchmark listed in the next section was run repeatedly on
each platform for a more or less long time window, depending on the benchmark,
to capture a diverse power trace and produce a high number of complete runs of all applications.
The results were averaged across the duration of the experiment.

Experiments on the intermittently-powered platform used the
WISP\,5.1~\cite{wisp5,wisp} RF-powered energy-harvesting device.
%
The WISP contains the MSP430FR5969~\cite{wolverine} MCU with 64\,kB of
non-volatile (FRAM) memory and 2\,kB of volatile (SRAM) memory and was
configured to 1\,MHz clock speed.
%
We powered the WISP using an RF signal generator emitting  a 20-\,dBm sinusoidal wave at 915\,MHz.
The signal generator was connected to the Liard RFMAX S9028PCRJ 8\,dBic
antenna~\cite{atlas2015}.
%
The antenna was oriented towards and in parallel with the WISP antenna, and
no objects obstructed the path.
%
We affixed the WISP with a paper harness at the edge of a table, so that the
WISP was parallel to the table surface at a height of 10\,cm.
%
For distance-controlled experiments we positioned the signal generator
antenna at a fixed distance from the WISP. The distances were $d=\{15, 30,
50\}$\,cm for the main experiments and 60\,cm for the task downscaling
experiments.
%
We chose relatively shorter distances than in a deployment scenario to reduce
charge time and run experiments faster, after having confirmed ourselves a
result also reported in prior work~\cite{alpaca} that the amount of energy
available in one charge cycle---the sum of stored energy and incoming energy
during execution---is the same at distances beyond 50\,cm where incoming energy
becomes negligible.
%
To obtain execution time, the software toggled GPIO pins at sections of the code
under profile, and the Saleae~\cite{saleae} logic analyzer measured
the interval between edges in the signal.

The experiments which are not sensitive to the behavior of an
energy-harvesting power supply were conducted on an MSP-EXP430FR5969
launchpad~\cite{MSP-EXP430FR5969_launchpad} board powered continuously with a
power supply.
%
This platform has the same MCU as the WISP.
%
Execution time was measured using the clock features in TI Code
Composer Studio IDE version 7.1.
%

>>>>

We used two platforms to evaluate \sys: (i) an \emph{intermittently-powered}
energy-harvesting device (WISP\,5.1~\cite{wisp5,wisp}), and (ii) a \emph{continuously-powered} evaluation
board (MSP-EXP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad}).
%
Every benchmark listed in the next section was run repeatedly on
each platform for a few minutes to ensure capturing a diverse power 
trace and produce a high number of complete runs of all applications.
The results were averaged across the duration of the experiment.

% Experiments on the intermittently-powered platform used the
% WISP\,5.1~\cite{wisp5,wisp} RF-powered energy-harvesting device.
%
The WISP contains the MSP430FR5969~\cite{wolverine} MCU with 64\,kB of
non-volatile (FRAM) memory and 2\,kB of volatile (SRAM) memory and was
configured to 1\,MHz clock speed.
%
We powered the WISP using an RF signal generator emitting  a 20\,dBm sinusoidal wave at 915\,MHz.
The signal generator was connected to the Liard RFMAX S9028PCRJ 8\,dBic
antenna~\cite{atlas2015}.
%
The antenna was oriented towards and in parallel with the WISP antenna, and
no objects obstructed the path.
%
We affixed the WISP with a paper harness at the edge of a table at a height of 10\,cm.
%
For distance-controlled experiments we positioned WISP at $d=\{15, 30,
50\}$\,cm from the exciter antenna and 60\,cm was used for the task downscaling
experiments.
%
% We chose relatively shorter distances than in a deployment scenario to reduce
% charge time and run experiments faster, after having confirmed ourselves a
% result also reported in prior work~\cite{alpaca} that the amount of energy
% available in one charge cycle---the sum of stored energy and incoming energy
% during execution---is the same at distances beyond 50\,cm where incoming energy
% becomes negligible.
%
To obtain execution time, the software toggled GPIO pins at sections of the code
under profile, and the Saleae~\cite{saleae} logic analyzer measured
the interval between edges in the signal. When the board is continously powered the 
execution time was measured using the clock features in TI Code Composer Studio IDE version 7.1.
%

### 2018-08-04 paper/asplos19/systemdescription.tex

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/overview.pdf}
	\caption{System's top-level view. \sys is composed of two core components: \emph{Adaptive Task Scheduler} and \emph{Virtual Memory Manager}.}
	\label{fig:system_overview}
\end{figure}
%
\sys is a new programming and execution model for intermittent computing on energy-harvesting devices. \sys addresses the challenges outlined in Section~\ref{sec:background} to make task-based intermittent programs {\em programmable} and {\em efficient}. \sys accomplishes this goal with a constellation of a new programming model and runtime software system support, that supports dynamically adaptive task-based execution. Fig.~\ref{fig:system_overview} shows an overview of \sys.

\textbf{Programming and Execution Model.}  To use \sys, a programmer must convert a plain C code into tasks by encapsulating the code in a top-level set of functions, sequences the control-flow between these tasks, and annotates memory accesses that manipulate global data.
The programmer compiles their task-based code, and links to \sys runtime,
producing a \sys-enabled binary. The runtime library relies on \sys's novel
{\em virtual memory manager} and its {\em adaptive task scheduler} to adapt its execution with the energy conditions.

\textbf{Adaptive Task Scheduler(ATS).} 
\sys's adaptive task scheduler (ATS) makes \emph{energy-aware} scheduling decisions to group tasks together or split a task. By coalescing tasks \sys amortizes commit and transition costs, and by a task splitting, after repeated failures on a single task, it avoids the task non-termination problem. The scheduler uses its recent execution history---no hardware dependency---as a metric to estimate energy availability and eventually to decide on the dynamic task size.

\textbf{Virtual Memory Manager (VMM).} \sys is able to efficiently coalesce
tasks because of its efficient virtual memory manager (VMM).
the VMM privatizes a group of memory pages demanded by a coalesced task, and limits an application access only to the fast volatile memory. It persists all pages modifications in non-volatile memory on a coalesced task transition. Section~\ref{sec:memory_virtulaization} provides details of VMM.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/overview.pdf}
	\caption{System's top-level view. \sys is composed of two core components: \emph{Adaptive Task Scheduler} and \emph{Virtual Memory Manager}.}
	\label{fig:system_overview}
\end{figure}
%
\sys is a new programming and execution model for intermittent computing on energy-harvesting devices. \sys addresses the challenges outlined in Section~\ref{sec:background} to make task-based intermittent programs {\em programmable} and {\em efficient}. \sys accomplishes this goal with a constellation of a new programming model and runtime software system support, that supports dynamically adaptive task-based execution. Fig.~\ref{fig:system_overview} shows an overview of \sys.\\
%
\textbf{Programming and Execution Model.}  To use \sys, a programmer must convert a plain C code into tasks by encapsulating the code in a top-level set of functions, sequences the control-flow between these tasks, and annotates memory accesses that manipulate global data.
The programmer compiles their task-based code, and links to \sys runtime,
producing a \sys-enabled binary. The runtime library relies on \sys's novel
{\em virtual memory manager} and its {\em adaptive task scheduler} to adapt its execution with the energy conditions.\\
%
\textbf{Adaptive Task Scheduler(ATS).} 
\sys's adaptive task scheduler (ATS) makes \emph{energy-aware} scheduling decisions to group tasks together or split a task. By coalescing tasks \sys amortizes commit and transition costs, and by a task splitting, after repeated failures on a single task, it avoids the task non-termination problem. The scheduler uses its recent execution history---no hardware dependency---as a metric to estimate energy availability and eventually to decide on the dynamic task size. \\
%
\textbf{Virtual Memory Manager (VMM).} \sys is able to efficiently coalesce
tasks because of its efficient virtual memory manager (VMM).
the VMM privatizes a group of memory pages demanded by a coalesced task, and limits an application access only to the fast volatile memory. It persists all pages modifications in non-volatile memory on a coalesced task transition. Section~\ref{sec:memory_virtulaization} provides details of VMM.
